\bf Focusing on Fast Neural Network Inference

### 2018-05-17 wnmt.2018/wnmt.tex
turn on timings

One approach is to use an off-the-shelf deep-learning toolkit such as Tensorflow\footnote{https://www.tensorflow.org/} or Pytorch\footnote{https://pytorch.org/} to train and do the inference where the novelty comes from selecting the appropriate models and tuning parameters within the toolkit for optimal performance.

>>>>

One approach is to use an off-the-shelf deep-learning toolkit to train and do the inference where the novelty comes from selecting the appropriate models and tuning parameters within the toolkit for optimal performance. % such as Tensorflow\footnote{https://www.tensorflow.org/} or Pytorch\footnote{https://pytorch.org/}
